Comparison among doublet predictions on benchmarking datasets

### 2024-06-17 analyses/doublet-detection/exploratory-notebooks/03_compare-benchmark-results.Rmd
remove pull_barcodes helper function

```{r}
pull_barcodes <- function(df, pred_var) {
  # Helper function to pull out barcodes for doublet calls
  df$barcodes[df[[pred_var]] == "doublet"]
}

upset_list <- doublet_df_list |>
  purrr::iwalk(
    \(df, dataset) {

      doublet_barcodes <- list(
        "scDblFinder" = pull_barcodes(df, "scdbl_prediction"),
        "scrublet"    = pull_barcodes(df, "scrublet_prediction"),
        "cxds"        = pull_barcodes(df, "cxds_prediction")
      )

>>>>

```{r}
upset_list <- doublet_df_list |>
  purrr::iwalk(
    \(df, dataset) {

      doublet_barcodes <- list(
        "scDblFinder" = df$barcodes[df$scdbl_prediction == "doublet"],
        "scrublet"    = df$barcodes[df$scrublet_prediction == "doublet"],
        "cxds"        = df$barcodes[df$cxds_prediction == "doublet"]
      )
